### 2016-08-03 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
small rephrasing of words

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{\bf Modelling creativity: identifying key components through a corpus based approach}
\textbf\newline{\sout{Creativity is what we say it is: identifying key components of creativity}}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Anna Jordanous\textsuperscript{1,\Yinyang, *},
Bill Keller\textsuperscript{2,\Yinyang}
\\
\bigskip
\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
\\
\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
\\
\bigskip

@@

The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus. This in turn can be regarded as providing evidence of which words are salient to the definition of creativity. Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}. It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}. This is a particular issue when analysing smaller corpora, such as those used in the present work (see Fig. 1). %\ref{S1_Fig}). 
The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information. By contrast, the $\chi^2$ statistic tends to under-emphasise such outliers at the expense of very frequently occurring data points.

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{\bf Modelling creativity: identifying key components through a corpus-based approach}
\textbf\newline{\sout{Creativity is what we say it is: identifying key components of creativity}}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Anna Jordanous\textsuperscript{1,\Yinyang, *},
Bill Keller\textsuperscript{2,\Yinyang}
\\
\bigskip
\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
\\
\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
\\
\bigskip

@@

The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus. This in turn can be regarded as providing evidence of which words are salient to the concept of creativity. Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}. It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}. This is a particular issue when analysing smaller corpora, such as those used in the present work (see Fig. 1). %\ref{S1_Fig}). 
The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information. By contrast, the $\chi^2$ statistic tends to under-emphasise such outliers at the expense of very frequently occurring data points.
